\chapter{Tawhid}

The point of the package is not to hide LaTeX from you. It is to move repeated
design logic into one place and keep the document entrypoint stable.

\section{What You Can Change}

You can adjust:

\begin{itemize}
  \item theme
  \item trim size
  \item chapter numbering style
  \item cover treatment
  \item running headers
\end{itemize}

\section{What You Still Control Directly}

You still write normal LaTeX content. If you need to extend the design, the
style file is a standard package and can be edited directly.

\section{Styled Source Text}

The package now includes dedicated environments for Qur'an, hadith, athar,
general Arabic blocks, and Arabic poetry, so recurring source-text patterns can
share one visual system.

\begin{quran}
إِنَّ مَعَ الْعُسْرِ يُسْرًا
\begin{translation}Indeed, with hardship comes ease.\end{translation}
\begin{reference}Surah al-Inshirah 94:6\end{reference}
\end{quran}

\begin{hadith}
إِنَّمَا الأَعْمَالُ بِالنِّيَّاتِ
\begin{translation}Actions are judged only by intentions.\end{translation}
\begin{reference}Sahih al-Bukhari 1\end{reference}
\begin{grade}Sahih\end{grade}
\end{hadith}

\begin{athar}
العِلْمُ قَبْلَ القَوْلِ وَالعَمَلِ
\begin{translation}Knowledge comes before speech and action.\end{translation}
\begin{reference}Reported from al-Bukhari in his chapter headings\end{reference}
\end{athar}

\begin{arabicblock}
هَذَا نَصٌّ عَرَبِيٌّ تَجْرِيبِيٌّ لِإِظْهَارِ تَنْسِيقِ الكُتْلَةِ العَرَبِيَّةِ العَامَّةِ.
\begin{translation}This is a short Arabic sample showing the generic Arabic block treatment.\end{translation}
\end{arabicblock}

\begin{poem}
أَلا كُلُّ شَيءٍ ما خَلا اللَهَ باطِلٌ & وَكُلُّ نَعيمٍ لا مَحالَةَ زائِلُ \\
وَكُلُّ أُناسٍ سَوفَ تَدخُلُ بَينَهُم & دُوَيهِيَّةٌ تَصفَرُّ مِنها الأَنامِلُ
\end{poem}
